---
title: "CV"
author: Haydeé Peruyero
date: "`r Sys.Date()`"
params:
  pdf_mode:
    value: true
output:
  pagedown::html_resume:
    css: ['dd_cv.css', 'resume']
    self_contained: true
---

```{css, echo=FALSE}
/* Turn-off side-bar for publications */
.pagedjs_page:not(:nth-of-type(-n+1)) {
  --sidebar-width: 0rem;
  --sidebar-background-color: #ffffff;
  --main-width: calc(var(--content-width) - var(--sidebar-width));
  --decorator-horizontal-margin: 0.2in;
}
```

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

library(magrittr)
library(knitr)
source("cv_printing_functions.r")

# Carga los datos de tu hoja de hoja de cálculo de google
#En este chunk sólo modifica la dirección de tu CV
CV <- create_CV_object(
  data_location = "https://docs.google.com/spreadsheets/d/1FMDzFXUOvlLltIFz8G9rzHk2dJkEDV1ObWGnu9Uha9g/edit?usp=sharing",  
  pdf_mode = params$pdf_mode
 )

```


```{r}
# Corrige la alinacion de los puntos
if(params$pdf_mode) {
    cat("
<style>
:root{
  --decorator-outer-offset-left: -6.5px;
}
</style>")
}
```


Aside
================================================================================
```{r}
## Construya una red interactiva de puestos coloreados por sección
# y conectados si ocurrieron en el mismo año
#datadrivencv::build_network_logo(CV$entries_data)
```



Contact {#contact}
--------------------------------------------------------------------------------
```{r informacion de contacto}
CV %>% print_contact_info()
```


Programming Languages {#skills}
--------------------------------------------------------------------------------

```{r}
CV %>% print_programming_languages()
```


Languages {#languages}
--------------------------------------------------------------------------------

```{r}
CV %>% print_languages()
```

About me {}
--------------------------------------------------------------------------------
I work at the intersection of geometry, topology, and bioinformatics, applying TDA and ML to explore patterns in biological data. I’m also passionate about teaching and programming.

<!--Disclaimer {#disclaimer}-->

Other CV Versions
--------------------------------------------------------------------------------

<!-- The source code is available at [HaydeePeruyero/CV](https://github.com/HaydeePeruyero/CV).  -->


The **short version** of my CV can be found in this link [Short CV](https://github.com/HaydeePeruyero/CV/blob/main/CV_pdf/CV_short_Nov2025.pdf)

The **Spanish simplified version** of my CV is available at this link [Spanish CV](https://github.com/HaydeePeruyero/CV/blob/main/CV_pdf/CV_Simplified_November2025.pdf)

<!-- The extended version of my CV can be found in this link [Extended CV](https://github.com/HaydeePeruyero/CV/blob/main/CV_HaydeePeruyero.pdf) -->

Last updated on `r Sys.Date()`.



Main
================================================================================

A. Haydeé Contreras Peruyero {#title} 
--------------------------------------------------------------------------------


<!-- My research interests lie at the intersection of geometry, topology, and bioinformatics. My work has focused on geometric group theory and the application of Topological Data Analysis (TDA) to problems in genomics, metagenomics, and pangenomics. I also use machine learning and statistics to explore structures in biological data. I have a strong passion for teaching, programming, and learning languages. -->





```{r}
# Note the special double pipe so we modify the CV object in place
CV %<>% print_text_block("intro") 
```






Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('education')
```

Appointments {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('appointments')
```

Publications{data-icon=book}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('academic_articles')
```

<!-- Relevant Publications for the Position {data-icon=book} -->
<!-- -------------------------------------------------------------------------------- -->

<!-- ```{r} -->
<!-- CV %<>% print_section('academic_articles') -->
<!-- ``` -->

<!--Other Publications {data-icon=book}-->
<!---------------------------------------------------------------------------------->

<!--```{r}-->
<!--CV %<>% print_section('academic_articles_no')-->
<!--```-->

Accepted papers {data-icon=book}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('accepted')
```

Preprints {data-icon=book}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('preprints')
```

<!-- Papers in preparation {data-icon=book} -->
<!-- -------------------------------------------------------------------------------- -->

<!-- ```{r} -->
<!-- CV %<>% print_section('in_preparation') -->
<!-- ``` -->

<!-- These breaks just force a new page so section doesnt get cut off -->
<br>
<br>
<br>

Teaching Experience {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('courses')
```

Short Courses and Workshops {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('mini_courses')
```

Thesis Supervision {data-icon=user-graduate data-concise=true}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('tesis_supervisor')
```

Commites {data-icon=search data-concise=true}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('commites')
```

Research Experience {data-icon=laptop}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('research_positions')
```

Talks and Posters {data-icon=comments}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('talks_and_posters')
```

Awards{data-icon=award}
--------------------------------------------------------------------------------
```{r}
CV %<>% print_section('awards')
```

Science Communication {data-icon=atom}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('science_communication')
```

Synergistic Activities {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('synergistic_activities')
```

Workshops and Courses Attended {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('course_attendances')
```


Certifications {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('certifications')
```


Training and work related to equality  {data-icon=balance-scale data-concise=true}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('courses_gender')
```


Additional Professional Training (Fieldwork Safety and First Aid) {data-icon=medkit}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('courses_health')
```


```{r}
CV %<>% print_links()
```




